### 2020-04-14 rR.tex
there's one thing that I'm missing...huh...

% Created by tikzDevice version 0.12.3 on 2020-04-09 18:48:49
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.31,247.68) --
	( 30.56,248.50) --
	( 33.80,249.34) --
	( 37.04,250.20) --
	( 40.29,251.09) --
	( 43.53,251.99) --
	( 46.78,252.92) --
	( 50.02,253.86) --
	( 53.26,254.83) --
	( 56.51,255.81) --
	( 59.75,256.82) --
	( 63.00,257.85) --
	( 66.24,258.90) --
	( 69.48,259.97) --
	( 72.73,261.06) --
	( 75.97,262.17) --
	( 79.22,263.30) --
	( 82.46,264.46) --
	( 85.70,265.64) --
	( 88.95,266.84) --
	( 92.19,268.05) --
	( 95.43,269.29) --
	( 98.68,270.54) --
	(101.92,271.81) --
	(105.17,273.11) --
	(108.41,274.42) --
	(111.65,275.76) --
	(114.90,277.13) --
	(118.14,278.52) --
	(121.39,279.93) --
	(124.63,281.37) --
	(127.87,282.82) --
	(131.12,284.29) --
	(134.36,285.79) --
	(137.61,287.30) --
	(140.85,288.84) --
	(144.09,290.41) --
	(147.34,292.01) --
	(150.58,293.64) --
	(153.82,295.30) --
	(157.07,296.99) --
	(160.31,298.71) --
	(163.56,300.44) --
	(166.80,302.19) --
	(170.04,303.97) --
	(173.29,305.78) --
	(176.53,307.62) --
	(179.78,309.49) --
	(183.02,311.40) --
	(186.26,313.35) --
	(189.51,315.33) --
	(192.75,317.36) --
	(196.00,319.41) --
	(199.24,321.50) --
	(202.48,323.61) --
	(205.73,325.76) --
	(208.97,327.95) --
	(212.21,330.17) --
	(215.46,332.42) --
	(218.70,334.72) --
	(221.95,337.06) --
	(225.19,339.44) --
	(228.43,341.86) --
	(231.68,344.31) --
	(234.92,346.79) --
	(238.17,349.31) --
	(241.41,351.87) --
	(244.65,354.47) --
	(247.90,357.09) --
	(251.14,359.76) --
	(254.39,362.46) --
	(257.63,365.21) --
	(260.87,367.98) --
	(264.12,370.80) --
	(267.36,373.65) --
	(270.60,376.54) --
	(273.85,379.47) --
	(277.09,382.43) --
	(280.34,385.43) --
	(283.58,388.46);
\definecolor{drawColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 27.31,247.65) --
	( 30.56,248.48) --
	( 33.80,249.33) --
	( 37.04,250.20) --
	( 40.29,251.09) --
	( 43.53,252.00) --
	( 46.78,252.94) --
	( 50.02,253.89) --
	( 53.26,254.86) --
	( 56.51,255.85) --
	( 59.75,256.87) --
	( 63.00,257.90) --
	( 66.24,258.95) --
	( 69.48,260.03) --
	( 72.73,261.12) --
	( 75.97,262.24) --
	( 79.22,263.38) --
	( 82.46,264.54) --
	( 85.70,265.72) --
	( 88.95,266.92) --
	( 92.19,268.14) --
	( 95.43,269.38) --
	( 98.68,270.63) --
	(101.92,271.91) --
	(105.17,273.21) --
	(108.41,274.52) --
	(111.65,275.86) --
	(114.90,277.23) --
	(118.14,278.62) --
	(121.39,280.03) --
	(124.63,281.47) --
	(127.87,282.92) --
	(131.12,284.38) --
	(134.36,285.87) --
	(137.61,287.38) --
	(140.85,288.91) --
	(144.09,290.47) --
	(147.34,292.06) --
	(150.58,293.68) --
	(153.82,295.34) --
	(157.07,297.03) --
	(160.31,298.74) --
	(163.56,300.47) --
	(166.80,302.22) --
	(170.04,304.00) --
	(173.29,305.80) --
	(176.53,307.64) --
	(179.78,309.51) --
	(183.02,311.41) --
	(186.26,313.36) --
	(189.51,315.34) --
	(192.75,317.37) --
	(196.00,319.42) --
	(199.24,321.50) --
	(202.48,323.61) --
	(205.73,325.76) --
	(208.97,327.94) --
	(212.21,330.16) --
	(215.46,332.42) --
	(218.70,334.72) --
	(221.95,337.06) --
	(225.19,339.44) --
	(228.43,341.86) --
	(231.68,344.32) --
	(234.92,346.81) --
	(238.17,349.33) --
	(241.41,351.90) --
	(244.65,354.49) --
	(247.90,357.13) --
	(251.14,359.80) --
	(254.39,362.51) --
	(257.63,365.26) --
	(260.87,368.04) --
	(264.12,370.87) --
	(267.36,373.73) --
	(270.60,376.62) --
	(273.85,379.56) --
	(277.09,382.53) --
	(280.34,385.54) --
	(283.58,388.58);
\definecolor{drawColor}{RGB}{86,180,233}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 27.31,247.64) --
	( 30.56,248.47) --
	( 33.80,249.33) --
	( 37.04,250.20) --
	( 40.29,251.09) --
	( 43.53,252.00) --
	( 46.78,252.94) --
	( 50.02,253.89) --
	( 53.26,254.86) --
	( 56.51,255.86) --
	( 59.75,256.87) --
	( 63.00,257.91) --
	( 66.24,258.96) --
	( 69.48,260.04) --
	( 72.73,261.13) --
	( 75.97,262.25) --
	( 79.22,263.39) --
	( 82.46,264.55) --
	( 85.70,265.73) --
	( 88.95,266.93) --
	( 92.19,268.15) --
	( 95.43,269.39) --
	( 98.68,270.65) --
	(101.92,271.92) --
	(105.17,273.22) --
	(108.41,274.54) --
	(111.65,275.88) --
	(114.90,277.24) --
	(118.14,278.63) --
	(121.39,280.04) --
	(124.63,281.48) --
	(127.87,282.92) --
	(131.12,284.39) --
	(134.36,285.87) --
	(137.61,287.38) --
	(140.85,288.91) --
	(144.09,290.47) --
	(147.34,292.05) --
	(150.58,293.67) --
	(153.82,295.33) --
	(157.07,297.02) --
	(160.31,298.73) --
	(163.56,300.45) --
	(166.80,302.20) --
	(170.04,303.97) --
	(173.29,305.78) --
	(176.53,307.61) --
	(179.78,309.47) --
	(183.02,311.38) --
	(186.26,313.32) --
	(189.51,315.31) --
	(192.75,317.33) --
	(196.00,319.38) --
	(199.24,321.47) --
	(202.48,323.58) --
	(205.73,325.73) --
	(208.97,327.92) --
	(212.21,330.14) --
	(215.46,332.40) --
	(218.70,334.70) --
	(221.95,337.05) --
	(225.19,339.44) --
	(228.43,341.86) --
	(231.68,344.33) --
	(234.92,346.82) --
	(238.17,349.36) --
	(241.41,351.93) --
	(244.65,354.54) --
	(247.90,357.18) --
	(251.14,359.87) --
	(254.39,362.59) --
	(257.63,365.35) --
	(260.87,368.14) --
	(264.12,370.98) --
	(267.36,373.85) --
	(270.60,376.76) --
	(273.85,379.71) --
	(277.09,382.70) --
	(280.34,385.72) --
	(283.58,388.79);
\definecolor{drawColor}{RGB}{0,158,115}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 27.31,247.64) --
	( 30.56,248.47) --
	( 33.80,249.32) --
	( 37.04,250.19) --
	( 40.29,251.09) --
	( 43.53,252.00) --
	( 46.78,252.94) --
	( 50.02,253.89) --
	( 53.26,254.86) --
	( 56.51,255.86) --
	( 59.75,256.87) --
	( 63.00,257.91) --
	( 66.24,258.97) --
	( 69.48,260.04) --
	( 72.73,261.14) --
	( 75.97,262.26) --
	( 79.22,263.40) --
	( 82.46,264.56) --
	( 85.70,265.74) --
	( 88.95,266.94) --
	( 92.19,268.16) --
	( 95.43,269.40) --
	( 98.68,270.66) --
	(101.92,271.93) --
	(105.17,273.23) --
	(108.41,274.55) --
	(111.65,275.89) --
	(114.90,277.25) --
	(118.14,278.64) --
	(121.39,280.05) --
	(124.63,281.48) --
	(127.87,282.93) --
	(131.12,284.39) --
	(134.36,285.88) --
	(137.61,287.38) --
	(140.85,288.91) --
	(144.09,290.46) --
	(147.34,292.05) --
	(150.58,293.67) --
	(153.82,295.32) --
	(157.07,297.01) --
	(160.31,298.72) --
	(163.56,300.44) --
	(166.80,302.19) --
	(170.04,303.96) --
	(173.29,305.76) --
	(176.53,307.59) --
	(179.78,309.45) --
	(183.02,311.35) --
	(186.26,313.30) --
	(189.51,315.28) --
	(192.75,317.31) --
	(196.00,319.36) --
	(199.24,321.45) --
	(202.48,323.57) --
	(205.73,325.72) --
	(208.97,327.91) --
	(212.21,330.14) --
	(215.46,332.41) --
	(218.70,334.71) --
	(221.95,337.07) --
	(225.19,339.46) --
	(228.43,341.90) --
	(231.68,344.37) --
	(234.92,346.88) --
	(238.17,349.42) --
	(241.41,352.01) --
	(244.65,354.63) --
	(247.90,357.28) --
	(251.14,359.98) --
	(254.39,362.71) --
	(257.63,365.49) --
	(260.87,368.30) --
	(264.12,371.15) --
	(267.36,374.05) --
	(270.60,376.98) --
	(273.85,379.94) --
	(277.09,382.95) --
	(280.34,385.99) --
	(283.58,389.07);
\definecolor{fillColor}{RGB}{230,159,0}

@@

\path[fill=fillColor] ( 35.86,253.72) --
	( 39.22,247.89) --
	( 32.49,247.89) --
	cycle;

\path[fill=fillColor] ( 44.40,256.16) --
	( 47.76,250.34) --
	( 41.03,250.34) --
	cycle;

\path[fill=fillColor] ( 52.94,258.73) --
	( 56.30,252.90) --
	( 49.58,252.90) --
	cycle;

\path[fill=fillColor] ( 61.48,261.41) --
	( 64.85,255.58) --
	( 58.12,255.58) --
	cycle;

\path[fill=fillColor] ( 70.02,264.21) --
	( 73.39,258.38) --
	( 66.66,258.38) --
	cycle;

\path[fill=fillColor] ( 78.57,267.14) --
	( 81.93,261.31) --
	( 75.20,261.31) --
	cycle;

\path[fill=fillColor] ( 87.11,270.19) --
	( 90.47,264.37) --
	( 83.75,264.37) --
	cycle;

\path[fill=fillColor] ( 95.65,273.40) --
	( 99.01,267.58) --
	( 92.29,267.58) --
	cycle;

\path[fill=fillColor] (104.19,276.77) --
	(107.56,270.94) --
	(100.83,270.94) --
	cycle;

\path[fill=fillColor] (112.74,280.26) --
	(116.10,274.43) --
	(109.37,274.43) --
	cycle;

\path[fill=fillColor] (121.28,283.89) --
	(124.64,278.06) --
	(117.91,278.06) --
	cycle;

\path[fill=fillColor] (129.82,287.67) --
	(133.18,281.85) --
	(126.46,281.85) --
	cycle;

\path[fill=fillColor] (138.36,291.63) --
	(141.73,285.80) --
	(135.00,285.80) --
	cycle;

\path[fill=fillColor] (146.90,295.78) --
	(150.27,289.96) --
	(143.54,289.96) --
	cycle;

\path[fill=fillColor] (155.45,300.06) --
	(158.81,294.24) --
	(152.08,294.24) --
	cycle;

\path[fill=fillColor] (163.99,304.54) --
	(167.35,298.72) --
	(160.63,298.72) --
	cycle;

\path[fill=fillColor] (172.53,309.20) --
	(175.89,303.38) --
	(169.17,303.38) --
	cycle;

\path[fill=fillColor] (181.07,314.20) --
	(184.44,308.38) --
	(177.71,308.38) --
	cycle;

\path[fill=fillColor] (189.62,319.33) --
	(192.98,313.51) --
	(186.25,313.51) --
	cycle;

\path[fill=fillColor] (198.16,324.68) --
	(201.52,318.86) --
	(194.79,318.86) --
	cycle;

\path[fill=fillColor] (206.70,330.22) --
	(210.06,324.39) --
	(203.34,324.39) --
	cycle;

\path[fill=fillColor] (215.24,336.05) --
	(218.61,330.22) --
	(211.88,330.22) --
	cycle;

\path[fill=fillColor] (223.78,342.17) --
	(227.15,336.34) --
	(220.42,336.34) --
	cycle;

\path[fill=fillColor] (232.33,348.47) --
	(235.69,342.65) --
	(228.96,342.65) --
	cycle;

\path[fill=fillColor] (240.87,355.10) --
	(244.23,349.27) --
	(237.51,349.27) --
	cycle;

\path[fill=fillColor] (249.41,361.97) --
	(252.77,356.14) --
	(246.05,356.14) --
	cycle;

\path[fill=fillColor] (257.95,369.32) --
	(261.32,363.50) --
	(254.59,363.50) --
	cycle;

\path[fill=fillColor] (266.50,376.85) --
	(269.86,371.02) --
	(263.13,371.02) --
	cycle;

\path[fill=fillColor] (275.04,384.53) --
	(278.40,378.70) --
	(271.67,378.70) --
	cycle;

\path[fill=fillColor] (283.58,392.80) --
	(286.94,386.97) --
	(280.22,386.97) --
	cycle;
\definecolor{fillColor}{RGB}{86,180,233}

@@

\path[fill=fillColor] ( 33.36,247.34) --
	( 38.35,247.34) --
	( 38.35,252.33) --
	( 33.36,252.33) --
	cycle;

\path[fill=fillColor] ( 41.90,249.78) --
	( 46.90,249.78) --
	( 46.90,254.78) --
	( 41.90,254.78) --
	cycle;

\path[fill=fillColor] ( 50.44,252.35) --
	( 55.44,252.35) --
	( 55.44,257.34) --
	( 50.44,257.34) --
	cycle;

\path[fill=fillColor] ( 58.98,255.03) --
	( 63.98,255.03) --
	( 63.98,260.02) --
	( 58.98,260.02) --
	cycle;

\path[fill=fillColor] ( 67.53,257.83) --
	( 72.52,257.83) --
	( 72.52,262.83) --
	( 67.53,262.83) --
	cycle;

\path[fill=fillColor] ( 76.07,260.76) --
	( 81.06,260.76) --
	( 81.06,265.75) --
	( 76.07,265.75) --
	cycle;

\path[fill=fillColor] ( 84.61,263.82) --
	( 89.61,263.82) --
	( 89.61,268.81) --
	( 84.61,268.81) --
	cycle;

\path[fill=fillColor] ( 93.15,267.03) --
	( 98.15,267.03) --
	( 98.15,272.03) --
	( 93.15,272.03) --
	cycle;

\path[fill=fillColor] (101.70,270.41) --
	(106.69,270.41) --
	(106.69,275.40) --
	(101.70,275.40) --
	cycle;

\path[fill=fillColor] (110.24,273.89) --
	(115.23,273.89) --
	(115.23,278.89) --
	(110.24,278.89) --
	cycle;

\path[fill=fillColor] (118.78,277.52) --
	(123.78,277.52) --
	(123.78,282.51) --
	(118.78,282.51) --
	cycle;

\path[fill=fillColor] (127.32,281.30) --
	(132.32,281.30) --
	(132.32,286.30) --
	(127.32,286.30) --
	cycle;

\path[fill=fillColor] (135.86,285.26) --
	(140.86,285.26) --
	(140.86,290.25) --
	(135.86,290.25) --
	cycle;

\path[fill=fillColor] (144.41,289.41) --
	(149.40,289.41) --
	(149.40,294.41) --
	(144.41,294.41) --
	cycle;

\path[fill=fillColor] (152.95,293.67) --
	(157.94,293.67) --
	(157.94,298.67) --
	(152.95,298.67) --
	cycle;

\path[fill=fillColor] (161.49,298.13) --
	(166.49,298.13) --
	(166.49,303.13) --
	(161.49,303.13) --
	cycle;

\path[fill=fillColor] (170.03,302.76) --
	(175.03,302.76) --
	(175.03,307.76) --
	(170.03,307.76) --
	cycle;

\path[fill=fillColor] (178.58,307.80) --
	(183.57,307.80) --
	(183.57,312.80) --
	(178.58,312.80) --
	cycle;

\path[fill=fillColor] (187.12,312.93) --
	(192.11,312.93) --
	(192.11,317.93) --
	(187.12,317.93) --
	cycle;

\path[fill=fillColor] (195.66,318.29) --
	(200.66,318.29) --
	(200.66,323.28) --
	(195.66,323.28) --
	cycle;

\path[fill=fillColor] (204.20,323.80) --
	(209.20,323.80) --
	(209.20,328.79) --
	(204.20,328.79) --
	cycle;

\path[fill=fillColor] (212.74,329.65) --
	(217.74,329.65) --
	(217.74,334.64) --
	(212.74,334.64) --
	cycle;

\path[fill=fillColor] (221.29,335.78) --
	(226.28,335.78) --
	(226.28,340.78) --
	(221.29,340.78) --
	cycle;

\path[fill=fillColor] (229.83,342.05) --
	(234.82,342.05) --
	(234.82,347.05) --
	(229.83,347.05) --
	cycle;

\path[fill=fillColor] (238.37,348.70) --
	(243.37,348.70) --
	(243.37,353.69) --
	(238.37,353.69) --
	cycle;

>>>>

% Created by tikzDevice version 0.12.3 on 2020-04-14 11:43:25
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 27.31,247.65) --
	( 30.56,248.50) --
	( 33.80,249.37) --
	( 37.04,250.25) --
	( 40.29,251.16) --
	( 43.53,252.09) --
	( 46.78,253.03) --
	( 50.02,254.00) --
	( 53.26,254.98) --
	( 56.51,255.98) --
	( 59.75,257.00) --
	( 63.00,258.04) --
	( 66.24,259.10) --
	( 69.48,260.18) --
	( 72.73,261.28) --
	( 75.97,262.40) --
	( 79.22,263.54) --
	( 82.46,264.70) --
	( 85.70,265.88) --
	( 88.95,267.07) --
	( 92.19,268.29) --
	( 95.43,269.52) --
	( 98.68,270.77) --
	(101.92,272.04) --
	(105.17,273.33) --
	(108.41,274.63) --
	(111.65,275.96) --
	(114.90,277.31) --
	(118.14,278.69) --
	(121.39,280.08) --
	(124.63,281.50) --
	(127.87,282.94) --
	(131.12,284.39) --
	(134.36,285.86) --
	(137.61,287.35) --
	(140.85,288.87) --
	(144.09,290.41) --
	(147.34,291.97) --
	(150.58,293.56) --
	(153.82,295.18) --
	(157.07,296.83) --
	(160.31,298.49) --
	(163.56,300.18) --
	(166.80,301.88) --
	(170.04,303.60) --
	(173.29,305.35) --
	(176.53,307.13) --
	(179.78,308.93) --
	(183.02,310.77) --
	(186.26,312.64) --
	(189.51,314.55) --
	(192.75,316.48) --
	(196.00,318.44) --
	(199.24,320.43) --
	(202.48,322.45) --
	(205.73,324.49) --
	(208.97,326.57) --
	(212.21,328.67) --
	(215.46,330.81) --
	(218.70,332.98) --
	(221.95,335.19) --
	(225.19,337.43) --
	(228.43,339.70) --
	(231.68,342.00) --
	(234.92,344.33) --
	(238.17,346.69) --
	(241.41,349.09) --
	(244.65,351.51) --
	(247.90,353.96) --
	(251.14,356.45) --
	(254.39,358.97) --
	(257.63,361.51) --
	(260.87,364.10) --
	(264.12,366.71) --
	(267.36,369.35) --
	(270.60,372.03) --
	(273.85,374.73) --
	(277.09,377.47) --
	(280.34,380.24) --
	(283.58,383.04);
\definecolor{drawColor}{RGB}{230,159,0}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 27.31,247.62) --
	( 30.56,248.48) --
	( 33.80,249.35) --
	( 37.04,250.25) --
	( 40.29,251.16) --
	( 43.53,252.10) --
	( 46.78,253.05) --
	( 50.02,254.02) --
	( 53.26,255.01) --
	( 56.51,256.02) --
	( 59.75,257.05) --
	( 63.00,258.09) --
	( 66.24,259.16) --
	( 69.48,260.24) --
	( 72.73,261.35) --
	( 75.97,262.47) --
	( 79.22,263.61) --
	( 82.46,264.77) --
	( 85.70,265.96) --
	( 88.95,267.16) --
	( 92.19,268.37) --
	( 95.43,269.61) --
	( 98.68,270.86) --
	(101.92,272.13) --
	(105.17,273.42) --
	(108.41,274.73) --
	(111.65,276.06) --
	(114.90,277.41) --
	(118.14,278.78) --
	(121.39,280.18) --
	(124.63,281.60) --
	(127.87,283.02) --
	(131.12,284.47) --
	(134.36,285.93) --
	(137.61,287.42) --
	(140.85,288.93) --
	(144.09,290.46) --
	(147.34,292.01) --
	(150.58,293.60) --
	(153.82,295.21) --
	(157.07,296.86) --
	(160.31,298.52) --
	(163.56,300.20) --
	(166.80,301.90) --
	(170.04,303.62) --
	(173.29,305.37) --
	(176.53,307.15) --
	(179.78,308.95) --
	(183.02,310.78) --
	(186.26,312.65) --
	(189.51,314.56) --
	(192.75,316.49) --
	(196.00,318.45) --
	(199.24,320.44) --
	(202.48,322.45) --
	(205.73,324.50) --
	(208.97,326.57) --
	(212.21,328.67) --
	(215.46,330.81) --
	(218.70,332.98) --
	(221.95,335.19) --
	(225.19,337.43) --
	(228.43,339.70) --
	(231.68,342.01) --
	(234.92,344.34) --
	(238.17,346.70) --
	(241.41,349.10) --
	(244.65,351.53) --
	(247.90,353.98) --
	(251.14,356.47) --
	(254.39,358.99) --
	(257.63,361.55) --
	(260.87,364.13) --
	(264.12,366.75) --
	(267.36,369.40) --
	(270.60,372.08) --
	(273.85,374.79) --
	(277.09,377.53) --
	(280.34,380.31) --
	(283.58,383.11);
\definecolor{drawColor}{RGB}{86,180,233}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 27.31,247.61) --
	( 30.56,248.47) --
	( 33.80,249.35) --
	( 37.04,250.24) --
	( 40.29,251.16) --
	( 43.53,252.10) --
	( 46.78,253.05) --
	( 50.02,254.02) --
	( 53.26,255.02) --
	( 56.51,256.03) --
	( 59.75,257.05) --
	( 63.00,258.10) --
	( 66.24,259.17) --
	( 69.48,260.25) --
	( 72.73,261.36) --
	( 75.97,262.48) --
	( 79.22,263.63) --
	( 82.46,264.79) --
	( 85.70,265.97) --
	( 88.95,267.17) --
	( 92.19,268.39) --
	( 95.43,269.63) --
	( 98.68,270.88) --
	(101.92,272.15) --
	(105.17,273.44) --
	(108.41,274.75) --
	(111.65,276.08) --
	(114.90,277.43) --
	(118.14,278.80) --
	(121.39,280.20) --
	(124.63,281.61) --
	(127.87,283.04) --
	(131.12,284.48) --
	(134.36,285.94) --
	(137.61,287.42) --
	(140.85,288.92) --
	(144.09,290.45) --
	(147.34,292.01) --
	(150.58,293.59) --
	(153.82,295.20) --
	(157.07,296.84) --
	(160.31,298.50) --
	(163.56,300.18) --
	(166.80,301.87) --
	(170.04,303.59) --
	(173.29,305.33) --
	(176.53,307.10) --
	(179.78,308.90) --
	(183.02,310.74) --
	(186.26,312.60) --
	(189.51,314.51) --
	(192.75,316.44) --
	(196.00,318.40) --
	(199.24,320.39) --
	(202.48,322.41) --
	(205.73,324.45) --
	(208.97,326.53) --
	(212.21,328.64) --
	(215.46,330.78) --
	(218.70,332.95) --
	(221.95,335.17) --
	(225.19,337.42) --
	(228.43,339.70) --
	(231.68,342.01) --
	(234.92,344.35) --
	(238.17,346.73) --
	(241.41,349.13) --
	(244.65,351.57) --
	(247.90,354.04) --
	(251.14,356.54) --
	(254.39,359.07) --
	(257.63,361.64) --
	(260.87,364.24) --
	(264.12,366.87) --
	(267.36,369.54) --
	(270.60,372.24) --
	(273.85,374.97) --
	(277.09,377.73) --
	(280.34,380.52) --
	(283.58,383.35);
\definecolor{drawColor}{RGB}{0,158,115}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 27.31,247.60) --
	( 30.56,248.46) --
	( 33.80,249.34) --
	( 37.04,250.24) --
	( 40.29,251.16) --
	( 43.53,252.09) --
	( 46.78,253.05) --
	( 50.02,254.02) --
	( 53.26,255.02) --
	( 56.51,256.03) --
	( 59.75,257.06) --
	( 63.00,258.11) --
	( 66.24,259.17) --
	( 69.48,260.26) --
	( 72.73,261.37) --
	( 75.97,262.49) --
	( 79.22,263.64) --
	( 82.46,264.80) --
	( 85.70,265.98) --
	( 88.95,267.18) --
	( 92.19,268.40) --
	( 95.43,269.64) --
	( 98.68,270.89) --
	(101.92,272.16) --
	(105.17,273.45) --
	(108.41,274.76) --
	(111.65,276.09) --
	(114.90,277.44) --
	(118.14,278.81) --
	(121.39,280.21) --
	(124.63,281.62) --
	(127.87,283.04) --
	(131.12,284.48) --
	(134.36,285.94) --
	(137.61,287.42) --
	(140.85,288.92) --
	(144.09,290.45) --
	(147.34,292.00) --
	(150.58,293.58) --
	(153.82,295.19) --
	(157.07,296.83) --
	(160.31,298.48) --
	(163.56,300.16) --
	(166.80,301.85) --
	(170.04,303.57) --
	(173.29,305.31) --
	(176.53,307.07) --
	(179.78,308.87) --
	(183.02,310.70) --
	(186.26,312.57) --
	(189.51,314.47) --
	(192.75,316.41) --
	(196.00,318.37) --
	(199.24,320.36) --
	(202.48,322.38) --
	(205.73,324.43) --
	(208.97,326.51) --
	(212.21,328.63) --
	(215.46,330.77) --
	(218.70,332.96) --
	(221.95,335.18) --
	(225.19,337.44) --
	(228.43,339.73) --
	(231.68,342.05) --
	(234.92,344.41) --
	(238.17,346.80) --
	(241.41,349.22) --
	(244.65,351.67) --
	(247.90,354.15) --
	(251.14,356.67) --
	(254.39,359.22) --
	(257.63,361.81) --
	(260.87,364.43) --
	(264.12,367.08) --
	(267.36,369.77) --
	(270.60,372.48) --
	(273.85,375.24) --
	(277.09,378.02) --
	(280.34,380.84) --
	(283.58,383.69);
\definecolor{fillColor}{RGB}{230,159,0}

@@

\path[fill=fillColor] ( 35.86,253.77) --
	( 39.22,247.94) --
	( 32.49,247.94) --
	cycle;

\path[fill=fillColor] ( 44.40,256.26) --
	( 47.76,250.43) --
	( 41.03,250.43) --
	cycle;

\path[fill=fillColor] ( 52.94,258.86) --
	( 56.30,253.03) --
	( 49.58,253.03) --
	cycle;

\path[fill=fillColor] ( 61.48,261.57) --
	( 64.85,255.75) --
	( 58.12,255.75) --
	cycle;

\path[fill=fillColor] ( 70.02,264.40) --
	( 73.39,258.58) --
	( 66.66,258.58) --
	cycle;

\path[fill=fillColor] ( 78.57,267.35) --
	( 81.93,261.52) --
	( 75.20,261.52) --
	cycle;

\path[fill=fillColor] ( 87.11,270.41) --
	( 90.47,264.59) --
	( 83.75,264.59) --
	cycle;

\path[fill=fillColor] ( 95.65,273.62) --
	( 99.01,267.79) --
	( 92.29,267.79) --
	cycle;

\path[fill=fillColor] (104.19,276.97) --
	(107.56,271.14) --
	(100.83,271.14) --
	cycle;

\path[fill=fillColor] (112.74,280.44) --
	(116.10,274.61) --
	(109.37,274.61) --
	cycle;

\path[fill=fillColor] (121.28,284.03) --
	(124.64,278.21) --
	(117.91,278.21) --
	cycle;

\path[fill=fillColor] (129.82,287.77) --
	(133.18,281.94) --
	(126.46,281.94) --
	cycle;

\path[fill=fillColor] (138.36,291.66) --
	(141.73,285.83) --
	(135.00,285.83) --
	cycle;

\path[fill=fillColor] (146.90,295.73) --
	(150.27,289.90) --
	(143.54,289.90) --
	cycle;

\path[fill=fillColor] (155.45,299.91) --
	(158.81,294.09) --
	(152.08,294.09) --
	cycle;

\path[fill=fillColor] (163.99,304.28) --
	(167.35,298.45) --
	(160.63,298.45) --
	cycle;

\path[fill=fillColor] (172.53,308.80) --
	(175.89,302.97) --
	(169.17,302.97) --
	cycle;

\path[fill=fillColor] (181.07,313.61) --
	(184.44,307.78) --
	(177.71,307.78) --
	cycle;

\path[fill=fillColor] (189.62,318.54) --
	(192.98,312.71) --
	(186.25,312.71) --
	cycle;

\path[fill=fillColor] (198.16,323.65) --
	(201.52,317.83) --
	(194.79,317.83) --
	cycle;

\path[fill=fillColor] (206.70,328.94) --
	(210.06,323.11) --
	(203.34,323.11) --
	cycle;

\path[fill=fillColor] (215.24,334.46) --
	(218.61,328.63) --
	(211.88,328.63) --
	cycle;

\path[fill=fillColor] (223.78,340.25) --
	(227.15,334.42) --
	(220.42,334.42) --
	cycle;

\path[fill=fillColor] (232.33,346.20) --
	(235.69,340.38) --
	(228.96,340.38) --
	cycle;

\path[fill=fillColor] (240.87,352.40) --
	(244.23,346.58) --
	(237.51,346.58) --
	cycle;

\path[fill=fillColor] (249.41,358.80) --
	(252.77,352.98) --
	(246.05,352.98) --
	cycle;

\path[fill=fillColor] (257.95,365.62) --
	(261.32,359.79) --
	(254.59,359.79) --
	cycle;

\path[fill=fillColor] (266.50,372.58) --
	(269.86,366.75) --
	(263.13,366.75) --
	cycle;

\path[fill=fillColor] (275.04,379.67) --
	(278.40,373.84) --
	(271.67,373.84) --
	cycle;

\path[fill=fillColor] (283.58,387.25) --
	(286.94,381.43) --
	(280.22,381.43) --
	cycle;
\definecolor{fillColor}{RGB}{86,180,233}

@@

\path[fill=fillColor] ( 33.36,247.39) --
	( 38.35,247.39) --
	( 38.35,252.38) --
	( 33.36,252.38) --
	cycle;

\path[fill=fillColor] ( 41.90,249.87) --
	( 46.90,249.87) --
	( 46.90,254.87) --
	( 41.90,254.87) --
	cycle;

\path[fill=fillColor] ( 50.44,252.48) --
	( 55.44,252.48) --
	( 55.44,257.47) --
	( 50.44,257.47) --
	cycle;

\path[fill=fillColor] ( 58.98,255.19) --
	( 63.98,255.19) --
	( 63.98,260.19) --
	( 58.98,260.19) --
	cycle;

\path[fill=fillColor] ( 67.53,258.02) --
	( 72.52,258.02) --
	( 72.52,263.02) --
	( 67.53,263.02) --
	cycle;

\path[fill=fillColor] ( 76.07,260.97) --
	( 81.06,260.97) --
	( 81.06,265.96) --
	( 76.07,265.96) --
	cycle;

\path[fill=fillColor] ( 84.61,264.04) --
	( 89.61,264.04) --
	( 89.61,269.03) --
	( 84.61,269.03) --
	cycle;

\path[fill=fillColor] ( 93.15,267.25) --
	( 98.15,267.25) --
	( 98.15,272.25) --
	( 93.15,272.25) --
	cycle;

\path[fill=fillColor] (101.70,270.62) --
	(106.69,270.62) --
	(106.69,275.61) --
	(101.70,275.61) --
	cycle;

\path[fill=fillColor] (110.24,274.08) --
	(115.23,274.08) --
	(115.23,279.08) --
	(110.24,279.08) --
	cycle;

\path[fill=fillColor] (118.78,277.67) --
	(123.78,277.67) --
	(123.78,282.67) --
	(118.78,282.67) --
	cycle;

\path[fill=fillColor] (127.32,281.40) --
	(132.32,281.40) --
	(132.32,286.40) --
	(127.32,286.40) --
	cycle;

\path[fill=fillColor] (135.86,285.29) --
	(140.86,285.29) --
	(140.86,290.28) --
	(135.86,290.28) --
	cycle;

\path[fill=fillColor] (144.41,289.36) --
	(149.40,289.36) --
	(149.40,294.36) --
	(144.41,294.36) --
	cycle;

\path[fill=fillColor] (152.95,293.52) --
	(157.94,293.52) --
	(157.94,298.51) --
	(152.95,298.51) --
	cycle;

\path[fill=fillColor] (161.49,297.85) --
	(166.49,297.85) --
	(166.49,302.85) --
	(161.49,302.85) --
	cycle;

\path[fill=fillColor] (170.03,302.34) --
	(175.03,302.34) --
	(175.03,307.33) --
	(170.03,307.33) --
	cycle;

\path[fill=fillColor] (178.58,307.20) --
	(183.57,307.20) --
	(183.57,312.19) --
	(178.58,312.19) --
	cycle;

\path[fill=fillColor] (187.12,312.13) --
	(192.11,312.13) --
	(192.11,317.12) --
	(187.12,317.12) --
	cycle;

\path[fill=fillColor] (195.66,317.25) --
	(200.66,317.25) --
	(200.66,322.24) --
	(195.66,322.24) --
	cycle;

\path[fill=fillColor] (204.20,322.50) --
	(209.20,322.50) --
	(209.20,327.49) --
	(204.20,327.49) --
	cycle;

\path[fill=fillColor] (212.74,328.04) --
	(217.74,328.04) --
	(217.74,333.04) --
	(212.74,333.04) --
	cycle;

\path[fill=fillColor] (221.29,333.85) --
	(226.28,333.85) --
	(226.28,338.85) --
	(221.29,338.85) --
	cycle;

\path[fill=fillColor] (229.83,339.77) --
	(234.82,339.77) --
	(234.82,344.76) --
	(229.83,344.76) --
	cycle;

\path[fill=fillColor] (238.37,345.99) --
	(243.37,345.99) --
	(243.37,350.98) --
	(238.37,350.98) --
	cycle;
